SDR enhancement by clouds

### 2024-04-02 article/article.Rmd
Commit 2024-04-02 12:14

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the atmosphere and biosphere. It drives and governs the climate
[@Gray2010].  It has direct practical application, in different industries, like
energy production and agriculture method.  The variability of its intensity, can
cause difficulties in predicting the yield and designing the appropriate equipment.
A lot of research has been focuces on predicting the renewable energy production in a
fine timescale and in near real-time (for a review see @Inman2013; @Graabak2016).

A big aspect of this variability are the interaction with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can enhance
the total shortwave irradiance reaching the ground. This effect can locally increase
the observed total shortwave irradiance higher than the expected clear sky irradiance
[see references therein].

Some of the proposed underling mechanisms of those events have been summarized by
@Gueymard2017, and include scattering on the edge of cumulus clouds or through thin
cirrus.  Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
The overall phenomenon depends on different interactive factors, that include cloud
thickness, constitution and type, and the relative position of the sun, the clouds,
and the observer [@Gueymard2017; @Veerman2022].  As such, there are multiple contributing mechanism that can create
the observed irradiance enhancements.

@@

The enhancements can effect the efficiency and stability of photovoltaic power
production [@Lappalainen2020; @Jaervelae2020].

And extreme enhancements cases have the potential to  compromise the integrity of the
infrastructure  [@DoNascimento2019].

Those enhancements have been reported to be able to exceed .... and duration.
For a list of recorded extreme cases
@Martins2022

The forward scattering of clouds near the sun has been observed to produce cases of
extreme enhancement irradiances [@Yordanov2015].

It has been reported than enhancements events can interfere in the comparison of
ground data and satellite observe ovations [@Damiani2018]

Instruments respose ....
@Martins2022

Methods of identification in the literature usually include the use of a simulated clear sky radiation
@Vamvakas2020; @Mol2023;

.... cite ....

...  reported trends ?...
.... cite ....

<!-- our work -->
In this study, we used modeled clear sky irradiance, in order to identify cloud
enhancement. We studied their occurrences, intensity and duration, in a thirty-year
period at the city of Thessaloniki. We were able to determine some trends of the
phenomenon, it's Climatology, and some of its general characteristics.

<!-- Define CE and ECE -->
In the relative bibliography different definition have been used for these events, some of
the are summarized by @Gueymard2017.
Here, we defined as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we defined as extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies, from instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

Characteristics of CE

Effects of clouds

- enhancement physics
- conditions
- other interferences

Identification methods from bib

@@

- data
- instrument
- location

Many have used models or some statistical method to determine then CE thresholds.

In this study, we evaluated the effects of the clouds on the total downward radiation
by studding the occurrences of the cloud enhancement cases, their intensity, and their
duration.  The recording of the radiation signal is the mean of one-minute. Thus, we
will refer to this time step as a cloud enhancement event (CE).

>>>>

The shortwave solar irradiance, reaching Earth's surface, is the main energy source
of the atmosphere and biosphere and drives and governs the climate [@Gray2010].  It
has direct practical application, in different industries, like energy production and
agriculture method.  The variability of its intensity, can cause difficulties in
predicting the yield, and designing the specifications of the appropriate equipment.
A lot of research has been focused on predicting the renewable energy production in a
fine timescale and in near real-time (for a review see @Inman2013; @Graabak2016).

A big aspect of this variability is the interaction with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can enhance
the total shortwave irradiance reaching the ground. This effect, can locally increase
the observed total shortwave irradiance higher than the expected clear sky irradiance
[see references therein].

Some of the proposed underling mechanisms of those events, have been summarized by
@Gueymard2017, and include scattering on the edge of cumulus clouds or through thin
cirrus.  Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
The overall phenomenon depends on different interactive factors, that include cloud
thickness, constitution and type; and the relative position of the sun, the clouds,
and the observer [@Gueymard2017; @Veerman2022].  As such, there are multiple
contributing mechanism that are responsible for the observed irradiance enhancements.

Cloud enhancements have been reported, to be able to exceed in intensity even the
value of the solar constant, resulting of clear indexes above unit. A summary of
extreme enchantment cases have been compiled by @Martins2022. There are also some
practical implication of the cloud enchantments.  The intensity and duration of
enhancements can effect the efficiency and stability of photovoltaic power production
[@Lappalainen2020; @Jaervelae2020], and extreme enhancements cases, have the
potential to compromise the integrity of photovoltaic plants infrastructure
[@DoNascimento2019].  It has also been demonstrated, that these events can interfere
in the comparison of ground data and satellite observations [@Damiani2018]

@@

<!--
Instruments respose ....
@Martins2022
-->

Methods of identification cloud enchantment events in the literature, usually include
the use of a simulated clear sky radiation as baseline, that is combined with an
appropriate threshold or some other statistical characteristics, and in some cases,
with visual methods with a sky cam [@Vamvakas2020; @Mol2023 and references therein].

<!-- our work -->
In this study, we evaluated the effects cloud enhancements on the total downward
radiation by studding the occurrences, their intensity, and their duration in a
thirty-year period at the city of Thessaloniki.  We used modeled clear sky
irradiance, as a baseline to identify cloud enhancements.  We were able to determine
some trends of the phenomenon, it's Climatology, and some of their  general
characteristics. We weren't able to find a comparable study that provides trends for
similar long term dataset, as ours.  The recording of the radiation signal is the
mean of one-minute. Thus, the minimum resolution of cloud enhancement events (CE), in
this study is one minute.

<!-- Define CE and ECE -->
In the relative bibliography different definition have been used for these events,
some of the are summarized by @Gueymard2017.  Here, we defined as cloud enhancement
events (CE) the cases when the measured global horizontal irradiance (GHI) at ground
level, exceeds the expected value under clear-sky conditions.  Similar, we define as
extreme cloud enhancement events (ECE), the cases when GHI, exceeds the Total Solar
Irradiance on horizontal plane at ground level.  Although the duration of these
bursts varies, from instantaneous to several minutes, here we are constrained by the
recorded data, to one-minute steps.

<!--
Identification methods from bib

@@

- data
- instrument
- location
-->

### 2024-04-02 article/article.tex
Commit 2024-04-02 12:14

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the atmosphere and biosphere. It drives and governs the climate
(Gray et al. 2010). It has direct practical application, in different industries, like
energy production and agriculture method. The variability of its intensity, can
cause difficulties in predicting the yield and designing the appropriate equipment.
A lot of research has been focuces on predicting the renewable energy production in a
fine timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).

A big aspect of this variability are the interaction with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can enhance
the total shortwave irradiance reaching the ground. This effect can locally increase
the observed total shortwave irradiance higher than the expected clear sky irradiance
{[}see references therein{]}.

Some of the proposed underling mechanisms of those events have been summarized by
Gueymard (2017), and include scattering on the edge of cumulus clouds or through thin
cirrus. Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015), through the clouds.
The overall phenomenon depends on different interactive factors, that include cloud
thickness, constitution and type, and the relative position of the sun, the clouds,
and the observer (Gueymard 2017; Veerman, Van Stratum, and Van Heerwaarden 2022). As such, there are multiple contributing mechanism that can create
the observed irradiance enhancements.

The enhancements can effect the efficiency and stability of photovoltaic power
production (Lappalainen and Kleissl 2020; Järvelä and Valkealahti 2020).

And extreme enhancements cases have the potential to compromise the integrity of the
infrastructure (Do Nascimento et al. 2019).

Those enhancements have been reported to be able to exceed \ldots. and duration.
For a list of recorded extreme cases
Martins, Mantelli, and Rüther (2022)

The forward scattering of clouds near the sun has been observed to produce cases of
extreme enhancement irradiances (Georgi Hristov Yordanov, Saetre, and Midtgård 2015).

It has been reported than enhancements events can interfere in the comparison of
ground data and satellite observe ovations (Damiani et al. 2018)

Instruments respose \ldots.
Martins, Mantelli, and Rüther (2022)

Methods of identification in the literature usually include the use of a simulated clear sky radiation
Vamvakas, Salamalikis, and Kazantzidis (2020); Mol, Knap, and Van Heerwaarden (2023);

\ldots. cite \ldots.

\ldots{} reported trends ?\ldots{}
\ldots. cite \ldots.

In this study, we used modeled clear sky irradiance, in order to identify cloud
enhancement. We studied their occurrences, intensity and duration, in a thirty-year
period at the city of Thessaloniki. We were able to determine some trends of the
phenomenon, it's Climatology, and some of its general characteristics.

In the relative bibliography different definition have been used for these events, some of
the are summarized by Gueymard (2017).
Here, we defined as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we defined as extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies, from instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

Characteristics of CE

Effects of clouds

\begin{itemize}
\tightlist
\item
  enhancement physics
\item
  conditions
\item
  other interferences
\end{itemize}

Identification methods from bib

\begin{itemize}
\tightlist
\item
  clearness index
\item
  modeled approaches
\item
  algorithmic id
\item
  AI
\item
  Visual
\end{itemize}

Constrains of the site

\begin{itemize}
\tightlist
\item
  data
\item
  instrument
\item
  location
\end{itemize}

Many have used models or some statistical method to determine then CE thresholds.

In this study, we evaluated the effects of the clouds on the total downward radiation
by studding the occurrences of the cloud enhancement cases, their intensity, and their
duration. The recording of the radiation signal is the mean of one-minute. Thus, we
will refer to this time step as a cloud enhancement event (CE).

>>>>

The shortwave solar irradiance, reaching Earth's surface, is the main energy source
of the atmosphere and biosphere and drives and governs the climate (Gray et al. 2010). It
has direct practical application, in different industries, like energy production and
agriculture method. The variability of its intensity, can cause difficulties in
predicting the yield, and designing the specifications of the appropriate equipment.
A lot of research has been focused on predicting the renewable energy production in a
fine timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).

A big aspect of this variability is the interaction with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can enhance
the total shortwave irradiance reaching the ground. This effect, can locally increase
the observed total shortwave irradiance higher than the expected clear sky irradiance
{[}see references therein{]}.

Some of the proposed underling mechanisms of those events, have been summarized by
Gueymard (2017), and include scattering on the edge of cumulus clouds or through thin
cirrus. Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015), through the clouds.
The overall phenomenon depends on different interactive factors, that include cloud
thickness, constitution and type; and the relative position of the sun, the clouds,
and the observer (Gueymard 2017; Veerman, Van Stratum, and Van Heerwaarden 2022). As such, there are multiple
contributing mechanism that are responsible for the observed irradiance enhancements.

Cloud enhancements have been reported, to be able to exceed in intensity even the
value of the solar constant, resulting of clear indexes above unit. A summary of
extreme enchantment cases have been compiled by Martins, Mantelli, and Rüther (2022). There are also some
practical implication of the cloud enchantments. The intensity and duration of
enhancements can effect the efficiency and stability of photovoltaic power production
(Lappalainen and Kleissl 2020; Järvelä and Valkealahti 2020), and extreme enhancements cases, have the
potential to compromise the integrity of photovoltaic plants infrastructure
(Do Nascimento et al. 2019). It has also been demonstrated, that these events can interfere
in the comparison of ground data and satellite observations (Damiani et al. 2018)

Methods of identification cloud enchantment events in the literature, usually include
the use of a simulated clear sky radiation as baseline, that is combined with an
appropriate threshold or some other statistical characteristics, and in some cases,
with visual methods with a sky cam (Vamvakas, Salamalikis, and Kazantzidis 2020; Mol, Knap, and Van Heerwaarden 2023 and references therein).

In this study, we evaluated the effects cloud enhancements on the total downward
radiation by studding the occurrences, their intensity, and their duration in a
thirty-year period at the city of Thessaloniki. We used modeled clear sky
irradiance, as a baseline to identify cloud enhancements. We were able to determine
some trends of the phenomenon, it's Climatology, and some of their general
characteristics. We weren't able to find a comparable study that provides trends for
similar long term dataset, as ours. The recording of the radiation signal is the
mean of one-minute. Thus, the minimum resolution of cloud enhancement events (CE), in
this study is one minute.

In the relative bibliography different definition have been used for these events,
some of the are summarized by Gueymard (2017). Here, we defined as cloud enhancement
events (CE) the cases when the measured global horizontal irradiance (GHI) at ground
level, exceeds the expected value under clear-sky conditions. Similar, we define as
extreme cloud enhancement events (ECE), the cases when GHI, exceeds the Total Solar
Irradiance on horizontal plane at ground level. Although the duration of these
bursts varies, from instantaneous to several minutes, here we are constrained by the
recorded data, to one-minute steps.
